Clustering time series based on probability distributions across temporal granularities

### 2021-10-31 main.Rmd
better wording for wpd based distance

>>>>

This distance metric considers two time series to be similar if the distributions of each category of an individual cyclic granularity or combination of categories for interacting cyclic granularities are similar. In this study, the distribution for each category is characterised using deciles (can potentially consider any list of quantiles), and the distances between distributions are calculated using the Jensen-Shannon distances (@Menendez1997-in), which are symmetric and thus could be used as a distance measure.

\noindent The sum of the distances between two series $x$ and $y$ in terms of cyclic granularity $A$ is defined as $$S^A_{x,y} = \sum_{j} D_{x,y}(A)$$ (sum of distances between each category $j$ of cyclic granularity $A$) or $$S^{A*B}_{x,y} = \sum_j \sum_k D_{x,y}(A, B)$$ (sum of distances between each combination of categories $(j, k)$ of the harmony $(A, B)$. After determining the distance between two series in terms of one granularity, we must combine them to produce a distance based on all significant granularities. When combining distances from individual $L$ cyclic granularities $C_l$ with $n_l$ levels,  $$S_{x, y} = \sum_lS^{C_l}_{x,y}/n_l$$ is employed, which is also a distance metric since it is the sum of JS distances.

Compute weighted pairwise distances $wpd$ (@Gupta2021-hakear) for all considered granularities for all observations. $wpd$ is designed to capture the maximum variation in the measured variable explained by an individual cyclic granularity or their interaction and is estimated by the maximum pairwise distances between consecutive categories normalised by appropriate parameters. A higher value of $wpd$ indicates that some interesting pattern is expected, whereas a lower value would indicate otherwise.

\noindent Once we have chosen $wpd$ as a relevant feature for characterizing the time series across one cyclic granularity, we have to decide how we combine differences between the multiple features (corresponding to multiple granularities) into a single number. The euclidean distance between them is chosen, with the granularities acting as variables and $wpd$ representing the value under each variable. With this approach, we should expect the observations with similar $wpd$ values to be clustered together. Thus, this approach is useful for grouping observations that have similar significance of patterns across different granularities. Similar significance does not imply similar pattern, which is where this technique varies from JS-based distances, which detect differences in patterns across categories.
